%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Nathan S. Ryan

\documentclass[margin,line]{resume}
\usepackage{bibentry}
\makeatletter\let\saved@bibitem\@bibitem\makeatother
\usepackage[breaklinks]{hyperref}
\def\UrlBreaks{\do\/\do-}
\makeatletter\let\@bibitem\saved@bibitem\makeatother
\usepackage{doi}
\hypersetup{
    colorlinks=true,%
    linkcolor=blue,%
    filecolor=magenta,%
    urlcolor=cyan,%
    breaklinks=true
}
\urlstyle{same}
\usepackage{xspace}
%\textheight=10.75in
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%

% Trying to bold my name in the bib
\usepackage{xstring}
\def\FormatName#1{%
  \IfSubStr{#1}{Ryan}{\textbf{#1}}{#1}%
}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Nathan S. Ryan}
\begin{resume}

%\bibliographystyle{katyunsrt}
\bibliographystyle{abbrvurl-huff}
\nobibliography{cv}

    % Contact Information
    \section{\mysidestyle Contact}
    mobile: (708) 567-0002 \hfill e-mail: \href{mailto:nathanryan.nuc@gmail.com}{nathanryan.nuc@gmail.com} \hfill website: \href{https://nsryan.github.io}{nsryan.github.io} \vspace{0mm}\\\vspace{1mm}%

    %__________________________________________________________________________________________________________________
    % Research Interests
    \vspace{-6mm}
    \section{\mysidestyle Research\\Interests}
                Nuclear fuel cycle simulation and analysis,
                energy system modeling, energy regulation, nuclear energy policy, environmental justice, decommissioning, and
                scientific computation.
                %
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle MS}
    \textbf{University of Illinois Urbana-Champaign},\hfill\textbf{Aug 2022 -- est. Dec 2024}\\
    \textsc{Nuclear, Plasma, and Radiological Engineering}\\
    % \begin{list2}
    %     \item Thesis: \emph{Optimization of Nuclear Fuel Cycle Transition Scenarios}
    %     \item Committee: Dr. Madicken Munk, Dr. Kathryn Huff
    % \end{list2}\vspace{-1.5mm}
    \vspace{-5.5mm}
    \section{\mysidestyle BS}
    \textbf{University of Illinois Urbana-Champaign},\hfill\textbf{Aug 2019 -- Aug 2022}\\
    \textsc{Engineering Physics}\vspace{-3mm}\\\vspace{-1mm}
    %__________________________________________________________________________________________________________________

% Research Experience
\section{\mysidestyle Research\\Experience}
\textbf{University of Illinois at Urbana-Champaign}, Urbana, IL \hfill \textbf{Aug 2022 -- Present} \\
\textsl{Graduate Research Assistant, Nuclear, Plasma, and Radiological Engineering} \\
\begin{itemize}
    \item Extended the Cyclus nuclear fuel cycle code to optimize space usage and enhanced core-loading control of assemblies.
    \item Engineered a rudimentary neural network from scratch and implemented a sophisticated PyTorch model to generate arbitrary-source weight windows for 2D Monte Carlo simulations, trained on my implementation of Legendre polynomial solutions to fixed-source problems.
    \item Evaluated international and national nuclear fuel cycle transition scenarios from traditional LWR technologies to TRISO fueled nuclear reactors, including separative work unit, energy production, and emissions calculations.
\end{itemize}
    \textsl{Undergraduate Research Assistant} \textsl{Advanced Reactors and Fuel Cycles}\hfill \textbf{May 2020 -- Aug 2022}\\
    \begin{itemize}
        \item Developed a deep-learning model for energy demand prediction and trained using microgrid data, resulting in enhanced model accuracy up to 7 Lyapunov time constants.
        \item Created robust testing suites for two projects using advanced PyTest features and developed Sphinx-based documentation following PEP-8 standards.
        \item Edited over 10 abstracts, theses, papers, and presentation materials for clarity, coherence, and academic rigor.
        \item Managed licensing for all group-generated code, ensuring compliance with CC-BY 4.0, BSD-3.0, MIT, GPLv3, and LGPLv3 licenses for both new and derivative projects.
    \end{itemize}

    \textbf{Oak Ridge National Laboratory}, Oak Ridge, TN \hfill \textbf{June 2024 -- August 2024} \\
    \textsl{Graduate Summer Intern, Research and Test Reactor Physics Group} \\
    \begin{itemize}
        \item Integrate enrichment versatility for non-equilibrium reactors into the Cyclus nuclear fuel cycle simulator.
    \end{itemize}

    %__________________________________________________________________________________________________________________
    % Honors and Awards
    \section{\mysidestyle Honors and\\Awards}
                NPRE, Students Award for Excellence in Graduate Service \hfill \textbf{2023}\vspace{.5mm}\\%
                ANS, Student Sections Committee Commendation for Service and Leadership \hfill \textbf{2023}\vspace{.5mm}\\%
                NPRE, Students Award for Excellence in Undergraduate Service \hfill \textbf{2022}\vspace{.5mm}\\%
                UIUC, Dean's List \hfill \textbf{2020}\vspace{.5mm}\\%
                Department of Physics, Excellence in Physics Award \hfill \textbf{2020}\vspace{.5mm}\\%

    \vspace{-4mm}
    \section{\mysidestyle Journal\\Publications}
      \begin{bibenum}
      \item \bibentry{bachmann_enrichment_2021}
      \end{bibenum}
    %__________________________________________________________________________________________________________________
    % Technical Reports
    \section{\mysidestyle Technical\\Reports}
    \begin{bibenum}
       \item \bibentry{dotson_economic_2021}
    \end{bibenum}
    %__________________________________________________________________________________________________________________
    % Poster Presentations
    \section{\mysidestyle Poster\\Presentations}
    \begin{bibenum}
        \item \bibentry{esom_stuco22}
        \item \bibentry{ever_ornl2024}
    \end{bibenum}
    %__________________________________________________________________________________________________________________
    % Other Publications
    \section{\mysidestyle Other\\Publications}
    % dissertations, capstones
    \begin{bibenum}
         \item \bibentry{restart_bas_2024}
    \end{bibenum}

    %__________________________________________________________________________________________________________________

    % Computer Skills
    \section{\mysidestyle Skills}
                \textbf{Coding Languages} \hfill bash, C++, Python, html, css, \LaTeX, BibTeX \vspace{.5mm}\\%
                \textbf{Build Systems} \hfill make, CMake\vspace{.5mm}\\%
                \textbf{Databases} \hfill SQL, SQLite\vspace{.5mm}\\%
                \textbf{Test Frameworks} \hfill PyTest\vspace{.5mm}\\%
                \textbf{Version Control} \hfill git\vspace{.5mm}\\%
                \textbf{Applications} \hfill Sphinx, Mathematica, PyTorch, Word, Excel, Powerpoint, cPanel\vspace{.5mm}%
    %__________________________________________________________________________________________________________________

    \section{\mysidestyle Professional\\Service}
    \textbf{Delegate}, Nuclear Engineering Student Delegation (NESD) \hfill \textbf{2023, 2024}\vspace{.5mm}\\%
    \begin{itemize}
        \item Developed policy statements covering the Nuclear Energy University Program (NEUP), regulatory reform, fuel cycle commercialization, trade programs, waste management, and international competition.
        \item Communicate the delegations vision with elected officials, non-governmental organizations, and commercial stakeholders in the nuclear industry.
    \end{itemize}
    \textbf{Organizer}, Young Professionals Congress (YPC), ANS \hfill \textbf{2022--2023}\vspace{.5mm}\\%
    \begin{itemize}
        \item Developed a plenary about transitions for former coal and natural gas communities.
        \item Curated the raffles, games, and professional development opprotunities for attendees.
    \end{itemize}
    \textbf{Public Relations Officer}, U. Illinois ANS student section  \hfill \textbf{2020--2022}\vspace{.5mm}\\%
    \begin{itemize}
        \item Coordinated phone banking, letter writing, and virtual meeting campaigns in support of the current fleet of reactors in Illinois and the end of Illinois' new nuclear moratorium.
        \item Developed and maintained relationships with local industry and state elected officials to advocate for nuclear energy and create professional development opportunities for our membership.
    \end{itemize}
    %__________________________________________________________________________________________________________________
\end{resume}

\end{document}


%______________________________________________________________________________________________________________________
% EOF

