%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Nathan S. Ryan

\documentclass[margin,line]{resume}
\usepackage{bibentry}
\makeatletter\let\saved@bibitem\@bibitem\makeatother
\usepackage[breaklinks]{hyperref}
\def\UrlBreaks{\do\/\do-}
\makeatletter\let\@bibitem\saved@bibitem\makeatother
\usepackage{doi}
\hypersetup{
    colorlinks=true,%
    linkcolor=blue,%
    filecolor=magenta,%
    urlcolor=cyan,%
    breaklinks=true
}
\urlstyle{same}
\usepackage{xspace}
%\textheight=10.75in
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%

% Trying to bold my name in the bib
\usepackage{xstring}
\def\FormatName#1{%
  \IfSubStr{#1}{Ryan}{\textbf{#1}}{#1}%
}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Nathan S. Ryan}
\begin{resume}

%\bibliographystyle{katyunsrt}
\bibliographystyle{abbrvurl-huff}
\nobibliography{cv}

    % Contact Information
    \section{\mysidestyle Contact}
    mobile: (708) 567-0002 \hfill e-mail: \href{mailto:nathanryan.nuc@gmail.com}{nathanryan.nuc@gmail.com} \hfill website: \href{https://nsryan.github.io}{nsryan.github.io} \vspace{0mm}\\\vspace{1mm}%

    %__________________________________________________________________________________________________________________
    % Research Interests
    \vspace{-6mm}
    \section{\mysidestyle Objective}
        Graduate with a strong background in nuclear engineering, focused on sustainable energy solutions. Passionate about advancing clean energy technologies such as nuclear reactors, hydrogen energy, and carbon management. Looking to apply my research, analytical, and communication skills to support the mission of the Office of Clean Energy Demonstrations and contribute to the future of energy.

                %
    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Key\\Skills}
        \textbf{Programming Languages} \hfill bash, C++, Python\vspace{.5mm}\\%
        \textbf{Build Systems} \hfill make, CMake\vspace{.5mm}\\%
        \textbf{Databases} \hfill SQL\vspace{.5mm}\\%
        \textbf{Other Tools} \hfill Sphinx, git, PyTest, \LaTeX, Mathematica\vspace{.5mm}%
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle MS}
    \textbf{University of Illinois Urbana-Champaign},\hfill\textbf{Aug 2022 -- est. Dec 2024}\\
    \textsc{Nuclear, Plasma, and Radiological Engineering}\\
    % \begin{list2}
    %     \item Thesis: \emph{Optimization of Nuclear Fuel Cycle Transition Scenarios}
    %     \item Committee: Dr. Madicken Munk, Dr. Kathryn Huff
    % \end{list2}\vspace{-1.5mm}
    \vspace{-5.5mm}
    \section{\mysidestyle BS}
    \textbf{University of Illinois Urbana-Champaign},\hfill\textbf{Aug 2019 -- Aug 2022}\\%
    \textsc{Engineering Physics}\\
    \vspace{-5mm}
    %__________________________________________________________________________________________________________________

    % Research Experience
    \section{\mysidestyle Experience}

    \textbf{University of Illinois at Urbana-Champaign}, Urbana, IL \hfill \textbf{Aug 2022 -- Present} \\
    \textsl{Graduate Research Assistant, Nuclear, Plasma, and Radiological Engineering} \\
    \begin{itemize}
        \item Conducted policy analysis and evaluated transition scenarios from traditional LWR reactors to TRISO-fueled reactors, influencing future regulatory considerations.
        \item Collaborated across technical teams to align policy advocacy with energy modeling and simulations, ensuring research informed real-world restrictions.
        \item Authored technical reports and publications, ensuring clarity and accessibility for both technical and non-technical audiences.
    \end{itemize}

    \textsl{Undergraduate Research Assistant} \textsl{Advanced Reactors and Fuel Cycles}\hfill \textbf{May 2020 -- Aug 2022}\\
    \begin{itemize}
        \item Collaborated with faculty to communicate the impact of nuclear energy policy and regulatory changes to students and external partners.
        \item Led the development of technical documents, ensuring all materials were clear, coherent, and aligned with academic rigor.
        \item Contributed to a deep-learning model for energy demand prediction, driving conversations around energy regulation and policy design.
    \end{itemize}

    \textbf{Oak Ridge National Laboratory}, Oak Ridge, TN \hfill \textbf{June 2024 -- August 2024} \\
    \textsl{Graduate Summer Intern, Research and Test Reactor Physics Group} \\
    \begin{itemize}
        \item Integrated non-equilibrium reactor enrichment models into the Cyclus fuel cycle simulator, advocating for clean energy innovations in both industry and policy forums.
        \item Enhanced communication of research results through technical presentations and reports for internal and external stakeholders and developed a framework to translate model outputs into recommendations for stakeholders.
    \end{itemize}

    \textbf{Nuclear Engineering Student Delegation} \hfill \textbf{2023, 2024} \\
    \textsl{NESD Delegate} \\
    \begin{itemize}
        \item Developed policy statements covering the Nuclear Energy University Program (NEUP), regulatory reform, fuel cycle commercialization, trade programs, waste management, and international cooperation.
        \item Communicated the delegation's vision of nuclear with elected officials, non-governmental organizations, and commercial stakeholders in the industry.
    \end{itemize}
%__________________________________________________________________________________________________________________
    \vspace{-4mm}
    \section{\mysidestyle Publications}
    % %\section{\mysidestyle Refereed\\Journal\\Publications} % also, vspace below

    \begin{bibenum}
        \item \bibentry{ever_ornl2024}
        \item \bibentry{esom_stuco22}
        \item \bibentry{bachmann_enrichment_2021}
        \item \bibentry{dotson_economic_2021}
    \end{bibenum}

    %__________________________________________________________________________________________________________________
    % Professional, Student Organizations
    \section{\mysidestyle Professional\\Service}

    \textbf{Organizer}, Young Professionals Congress (YPC), ANS \hfill \textbf{2022--2023}\vspace{.5mm}\\%
    \begin{itemize}
        \item Developed a plenary about transitions for former coal and natural gas communities.
        \item Created communication strategies to promote engaging policy discussions for attendees in the nuclear energy sector.
    \end{itemize}

    \textbf{Public Relations Officer}, U. Illinois ANS student section  \hfill \textbf{2020--2022}\vspace{.5mm}\\%
    \begin{itemize}
        \item Coordinated phone banking, letter writing, and virtual meeting campaigns in support of the current fleet of reactors in Illinois and the end of Illinois' nuclear moratorium.
        \item Initiated and maintained relationships with local industry and state elected officials to advocate for nuclear energy and create professional development opportunities for our membership.
    \end{itemize}

\end{resume}

\end{document}


%______________________________________________________________________________________________________________________
% EOF

